\documentclass{article}
\usepackage[paper=a4paper,margin=0.75in]{geometry}
\usepackage{listings}
\usepackage{color}
\usepackage{graphicx}
\usepackage{amsmath}
\graphicspath{ {images/} }
 
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
  backgroundcolor=\color{backcolour},   
  commentstyle=\color{codegreen},
  keywordstyle=\color{blue},
  numberstyle=\tiny\color{codegray},
  stringstyle=\color{codepurple},
  basicstyle=\footnotesize,
  breakatwhitespace=false,         
  breaklines=true,                 
  captionpos=b,                    
  keepspaces=true,                 
  numbers=left,                    
  numbersep=5pt,                  
  showspaces=false,                
  showstringspaces=false,
  showtabs=false,                  
  tabsize=2
}
 
\lstset{style=mystyle}

\begin{document}
  \null\hfill
  \begin{tabular}[t]{l@{}}
    \textbf{Todd Vorisek}\\
    \textbf{Jason Hsi} \\
    CS 372 \\
    Homework 1\\
    \textit{Feb 7, 2018} \\
  \end{tabular}\\

  \section*{Feb 7, 2018}
    Time logged: $2 \times 1 $ hours
    \begin{itemize}
      \item Set up server and EC2 instance.
    \end{itemize}

  \section*{Feb 13, 2018}
    Time logged: $2.5 \times 2 $ hours
    \begin{itemize}
      \item Wrote ship class. 
      \item Started Battleship Game class. 
      \item Wrote ShipCreation, ShipHits, and BattleshipGameCreation tests.
    \end{itemize}

  \section*{Feb 18, 2018}
    Time logged: $2.5 \times 2 $ hours
    \begin{itemize}
      \item More or less finished the game class.
      \item Minor refactor and broke some logic out into smaller functions.
      \item Started game loop.
      \item Started interface integration.
    \end{itemize}

  \section*{Feb 25, 2018}
    Time logged: $3 \times 1 $ hours
    \begin{itemize}
      \item Fixed message passing for firing code.
      \item Got game initialization and game over states working.
      \item Finalized interface.
      \item Hacked in ugly bit of code to get it playable for demo day.
    \end{itemize}

\end{document}